A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM). Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction. The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}. This implies that an original system exists with more detailed information. Figure~\ref{fig:IllustrationMOR} presents an interpretation of MOR concept in which a graphical representation of a rabbit is reconstructed with a reduced number of facets (rhs of this illustration).

@@

The research focuses on reducing the order of the permeability field. Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field. The mathematical model is discretized by a novel high-order accurate control volume finite element method (CVFEM) (see \cite{Gomes_2017} for further details of the model formulation) which couples both the fine resolution and upscaled representation of the permeability field. Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to analyse the various upscaling techniques used.

>>>>

\medskip
{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM). Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction. The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}. This implies that an original system exists with more detailed information. Figure~\ref{fig:IllustrationMOR} presents an interpretation of MOR concept in which a graphical representation of a rabbit is reconstructed with a reduced number of facets (rhs of this illustration).

@@

\bigskip
This work focuses on reducing the order of permeability field distribution for multiphase flow simulations in porous media. Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field. The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) which couples both the fine resolution and upscaled representation of the permeability field. Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to analyse the various upscaling techniques used.
